%====================================================
%  Disclaimer
%====================================================
\documentclass[
    aps,
    prd,
    twocolumn,
    nofootinbib,
    floatfix,
    superscriptaddress
]{revtex4-2}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{mathtools}
\usepackage{physics}
\usepackage{bm}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{microtype}
\usepackage{enumitem}
\setlist{nosep}
\usepackage[
    colorlinks=true,
    linkcolor=blue,
    citecolor=blue,
    urlcolor=blue
]{hyperref}

%===================================================

\begin{document}

\title{Gamma-ray Analysis for Multi-Messenger Astrophysics: GAMMA}

\author{Joan Alcaide-Núñez}
\affiliation{Ludwig-Maximilian-Universität München (LMU München), Munich, Germany}

\author{Martina Solano Soto}
\affiliation{affil}

\date{\today}

\maketitle

% Abstract
\begin{abstract}
	Abstract.
\end{abstract}

\tableofcontents
\vspace{1em}

%====================================================
\section{Introduction}
The Gamma-ray Analysis for Multi-Messenger Astrophysics (GAMMA) initiative is a project by the CAPIBARA Collaboration with the goal to study the high-energy, gamma-ray phenomena in the universe and launch a CubeSat to observe these events. In this white paper, we provide a set of compelling open problems that motivate the development and launch of such a mission.

In the 2020 decadal survey \cite{missing}, it was pointed out that multi-band, that means acros the electromagnetic spectrum, and multi-messenger, that means combining different "messengers" such as light, GW and neutrino, detections were to be prioritized in the next years. Currently operating flagship gamma-ray observatories have long passed their main operation lifetimes, and new replacements are still in very early phases.

Professionally or student developed CubeSats with miniaturized detector technology have proven to be able to successfully detect gamma-ray bursts (GRBs) \cite{EIRSAT-1, GRBalpha, HERMES, BurstCube}. However, gamma-ray photons cannot be focused as with a traditional optical telescope. A good way around to accurately observing and locating GRBs is to perform triangulation with multiple satellites in orbit. Therefore, having multiple missions with large fields of view and good resolution capabilities is of very much importance for the proper study of this astrophysical phenomena.

Missing clear explanation of what are gamma-ray bursts and why we need to send detectors to orbit?


%====================================================
\section{Multi-Messenger Astronomy}



%====================================================
\section{Cosmology: GRBs as High-$z$ Probes}


\begin{itemize}
	\item intro to cosmology: the LambdaCDM model as the model of the universe (explaining accelerated expansion from EFE)
	\item explain the problem of the Hubble tension (what is wrong with our current standard model of the universe?)
	\item how GRB can be used to probe the high-z redshift, why does it matter to probe high-z and what do we need in terms of instrumentation
\end{itemize}


%====================================================
\section{Lorentz Invariance and High-Energy Photon Lags}

\begin{itemize}
	\item briefly explain why a theory of quantum gravity is of such relevance
	\item elaborate on how detecting high-energy photon lags provides direct proof of a granular space-time
	\item transform theory into timing requirements
\end{itemize}


%====================================================
\section{Summary of technical requirements}

% insert table


%====================================================
\section{Conclusions}

% Acknowledgments

\begin{acknowledgments}
	We are grateful to the members of the CAPIBARA Collaboration for useful discussions and feedback. The authors are happy to receive feedback: \href{https://capibara3.github.io/contact.html}{contact us}.
\end{acknowledgments}

% Bibliography
\bibliographystyle{apsrev4-2}
\bibliography{references}

\end{document}
